---
title: "R Notebook"
output: html_notebook
---



### Take a generative model for a spin
To the right you have the R code that implements the generative model we just developed.

* Run this code to generate a simulated dataset. Assume the underlying proportion of success of curing a zombie is 42% and that you administer the drug to 100 zombies.

* Instead of representing cured zombies as a vector of 1s and 0s it could be represented as a count of the number of cured out of the total number of treated. 

```{r}
# Parameters
prop_success <- 0.42
n_zombies <- 100

# Simulating data
data <- c()
for(zombie in 1:n_zombies) {
  data[zombie] <- runif(1, min = 0, max = 1) < prop_success
}
data <- as.numeric(data)
data <- sum(data)
```

### Take the binomial distribution for a spin

It turns out that the generative model you ran last exercise already has a name. It's called the binomial process or the binomial distribution. In R you can use the rbinom function to simulate data from a binomial distribution. The rbinom function takes three arguments:

* n The number of times you want to run the generative model
* size The number of trials. (For example, the number of zombies you're giving the drug.)
* prob The underlying proportion of success as a number between 0.0 and 1.0.

(Video aquí)

### How many visitors could your site get (1)?

To get more visitors to your website you are considering paying for an ad to be shown 100 times on a popular social media site. According to the social media site, their ads get clicked on 10% of the time.

```{r}
# Fill in the parameters
n_samples <- 100000
n_ads_shown <- 100
proportion_clicks <- 0.1
n_visitors <- rbinom(n_samples, size = n_ads_shown, 
                     prob = proportion_clicks)

# Visualize n_visitors
hist(n_visitors)
```
  

### Adding a prior to the model

You're not so sure that your ad will get clicked on exactly 10% of the time. Instead of assigning proportion_clicks a single value you are now going to assign it a large number of values drawn from a probability distribution. 

```{r}
# Update proportion_clicks
n_samples <- 100000
n_ads_shown <- 100
proportion_clicks <- runif(n = n_samples, min = 0.0, max = 0.2)
n_visitors <- rbinom(n = n_samples, size = n_ads_shown, prob = proportion_clicks)

# Visualize the results
hist(proportion_clicks)
hist(n_visitors)
```


### Update a Bayesian model with data

You ran your ad campaign, and 13 people clicked and visited your site when the ad was shown a 100 times. You would now like to use this new information to update the Bayesian model.

* The model you put together in the last exercise resulted in two vectors: (1) `proportion_clicks` that represents the uncertainty regarding the underlying proportion of clicks and (2) `n_visitors` which represents the uncertainty regarding the number of visitors you would get. We have now put these vectors into a data frame for you called prior.


Bayes is flexible

    You can include information sources in addition to the data.
    You can make any comparisons between groups or data sets.
    You can use the result of a Bayesian analysis to do Decision Analysis.
    You can change the underlying statistical model.



